Implications of afforestation policies for global markets

### 2024-02-28 paper.Rmd
Update paper.Rmd

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any price impacts that are beneficial for consumers resulting from this policy, with the price of agricultural goods decreasing 0.3 percent (Table 6). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.3 and 5.1 percent.

>>>>

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any price impacts that are beneficial for consumers resulting from this policy, with the price of agricultural goods decreasing 0.3 percent (Table \@ref(tab:pm)). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.3 and 5.1 percent.

```{r echo= FALSE}
baselineGTAP = HARr::read_SL4('asset/GTAP/run_baseline.sl4')
worldGTAP = HARr::read_SL4('asset/GTAP/run_scenario1.sl4')

out = ((1+worldGTAP$pm/100)/(1+baselineGTAP$pm/100)-1)

colnames(out) = regLabels[colnames(out)]
out = cbind(out, Total = rowSums(out))

kableExtra::column_spec(
  kableExtra::column_spec(kableExtra::kable_styling(
    knitr::kable(out, caption = 'Percent change in market prices for agricultural goods in 2033, in dollars, with deforestation mitigation policy in place', digits = 1, escape = FALSE, label = 'pm')
  ), 1, border_left = TRUE),
  5,
  border_right = TRUE
)
